Self Regulation Ontology Retest Analyses

### 2018-12-18 code/analysis_nbs/ResponseToReviewers.Rmd

---
title: 'SRO Retest Response to Reviewers'
output:
github_document:
toc: yes
toc_float: yes
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
from_gh=FALSE
script_loader = function(file, path, remote=from_gh, branch="master"){
  if(remote){
    library(RCurl)
    gh_path = paste('https://raw.githubusercontent.com/zenkavi',
                     strsplit(path, '/')[[1]][1],
                     branch,
                     paste(strsplit(path, '/')[[1]][-1],'/',sep = '', collapse=""),
                    sep="/")
    eval(parse(text = getURL(paste0(gh_path, file), ssl.verifypeer = FALSE)))
  }else{
    source(paste0('/Users/zeynepenkavi/Dropbox/PoldrackLab/',path, file))
  }
}

### 2018-12-18 code/SRO_Retest_Analyses.Rmd
working on reviewer responses

```{r}
demog_boot_df %>%
  group_by(dv) %>%
  summarise(median_icc = quantile(icc, probs=0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975)) %>%
  arrange(-median_icc)
```

@@

```{r}
demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc'))

demog_rel_df %>%
  select(dv, icc) %>%
  arrange(-icc)
```

@@

demog_rel_df %>%
  mutate(timed = ifelse(dv %in% timed_demogs, 1, 0)) %>%
  ggplot(aes(icc, fill = factor(timed)))+
  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
  xlab("ICC")+
  ylab("Count")+
  scale_fill_manual(values = c("grey", "grey25"))+
  theme(legend.position = "none")
```

@@

for(i in 1:length(numeric_cols)){
  tmp = match_t1_t2(numeric_cols[i],format='wide')
  tmp = tmp %>%
  mutate(difference = scale(`2` - `1`))
  t1_2_difference = rbind(t1_2_difference, tmp)
}

@@

```{r}
tmp = duplicate_items %>%
  select(similarity, t1_t1_polycor, t2_t2_polycor) %>%
  gather(key, value, -similarity)

@@

```{r eval=FALSE, echo=FALSE}
summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000))
```

@@

```{r}
summary(rel_comp$sample_size[rel_comp$task == "survey"])
summary(rel_comp$sample_size[rel_comp$task == "task"])

rel_comp %>%
  group_by(task) %>%
  summarise(mean_sample_size = mean(sample_size),
            sem_sample_size = sem(sample_size)) %>%
  ggplot(aes(task,mean_sample_size,col=task))+
  geom_point(size=5)+
  geom_errorbar(aes(ymin=mean_sample_size-sem_sample_size, ymax=mean_sample_size+sem_sample_size), width = 0, size=2)+
  xlab("")+
  ylab("Sample size")+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))
```

@@

```{r}
rel_comp %>%
  ggplot(aes(task, retest_reliability, fill = task))+
  geom_boxplot()+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  xlab("")+
  ylab("Mean ICC")+
  ylim(-0.4,1)
```

@@

lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)

write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
```

@@

sample one row per measure out of lit review
r^2 of retest_reliability ~ sampled_reliability vs.
r^2 of retest_reliability ~ mean_icc

coef of retest_reliability ~ sampled_reliability vs.
coef of retest_reliability ~ mean_icc

@@

comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))

write.csv(comp_lit_pred_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
```

@@

Though we are primarily reporting ICC's as our metric of reliability the results don't change depending on the metric chosen. Here we plot point estimates of three different reliability metrics against each other (ICC, Pearson, Spearman). The bootstrapped version is essentially the same but the plots are busier due to more datapoints.

```{r}
rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))

rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df[grep('holt', rel_df$dv), 'task'] = "task"
rel_df = rel_df %>%
  select(dv, task, spearman, icc, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
```

@@

```{r}
cor(rel_df[,c('spearman', 'icc', 'pearson')])
```

Note: Some variables have <0 ICC's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.

@@

```{r message=FALSE, warning=FALSE}
boot_df %>%
  group_by(dv) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

@@

boot_df %>%
  group_by(task) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r eval=FALSE}
summary(icc_by_task_model)
```

@@

@@

The quantiative explanation for the difference in reliability estimates between surveys and tasks, as recently detailed by Hedge et al. (2017), lies in the difference in sources of variance between these measures. Specifically, the ICC is calculated as the ratio of variance between subjects variance to all sources of variance. Thus, measures with high between subjects variance would have high test-retest reliability. Intuitively, measures with high between subjects variance are also better suited for individual difference analyses as they would capture the differences between the subjects in a sample.

@@

summary(var_subs_pct_by_task_model)
```

@@

```{r}
summary(var_ind_pct_by_task_model)
```

```{r}
summary(var_resid_pct_by_task_model)
```

@@

knitr::include_graphics(paste0(fig_path, fig_name))
```
## Task Reliabilities

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_icc','icc_2.5','icc_97.5'), digits=3)
```

@@

Does number of items in a task have a significant effect on the average ICC of meaningful measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

summary(icc_by_num_trials_model)
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1,
         rt_acc != 'other') %>%
  drop_na() %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv')

tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc_median = quantile(icc, probs = 0.5),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_vars = n()/1000)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('icc_median', 'icc_2.5', 'icc_97.5'), digits=3)
```

@@

```{r}
summary(lmerTest::lmer(icc ~ contrast + (1|dv) ,tmp))
# summary(MCMCglmm(icc ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
```

@@

```{r}
summary(icc_by_rawfit_noncon_model)
```

@@

```{r}
summary(icc_by_rawfit_con_model)
```

@@

```{r}
tmp %>%
  group_by(contrast) %>%
  summarise(mean_icc = mean(icc),
            sd_icc = sd(icc))
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  left_join(boot_df[,c("dv", "icc")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

tmp_save = tmp %>%
  group_by(task_name) %>%
  summarise(median_icc = median(icc),
            icc_2.5 = quantile(icc, probs = 0.025),
            icc_97.5 = quantile(icc, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('median_icc', 'icc_2.5','icc_97.5'), digits=3)
```

@@

Does number of items in a survey have a significant effect on the average ICC of survey measures? No.

```{r warning=FALSE, message=FALSE}
summary(lmerTest::lmer(icc ~ num_all_trials + (1|dv), data = tmp))
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("ICC")
```

>>>>

```{r}
demog_boot_df %>%
  group_by(dv) %>%
  summarise(median_icc2.1 = quantile(icc2.1, probs=0.5),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975)) %>%
  arrange(-median_icc2.1)
```

@@

```{r}
demog_rel_df = make_rel_df(test_demog, t2_df = retest_demog, metrics=c('icc2.1'))

demog_rel_df %>%
  select(dv, icc2.1) %>%
  arrange(-icc2.1)
```

@@

demog_rel_df %>%
  mutate(timed = ifelse(dv %in% timed_demogs, 1, 0)) %>%
  ggplot(aes(icc2.1, fill = factor(timed)))+
  geom_histogram(position = "identity", alpha = 0.7, color = NA)+
  xlab("icc2.1")+
  ylab("Count")+
  scale_fill_manual(values = c("grey", "grey25"))+
  theme(legend.position = "none")
```

@@

for(i in 1:length(numeric_cols)){
  tmp = match_t1_t2(numeric_cols[i],t1_df=test_data ,t2_df=retest_data,format='wide')
  tmp = tmp %>%
  mutate(difference = scale(`2` - `1`))
  t1_2_difference = rbind(t1_2_difference, tmp)
}

@@

```{r message=FALSE}
tmp = duplicate_items %>%
  select(similarity, t1_t1_polycor, t2_t2_polycor) %>%
  gather(key, value, -similarity)

@@

```{r eval=FALSE, echo=FALSE}
# summary(MCMCglmm(value ~ key*scale(similarity), data=tmp, nitt = 50000))
```

@@

```{r}
summary(rel_comp$sample_size[rel_comp$task == "survey"])
summary(rel_comp$sample_size[rel_comp$task == "task"])
```

```{r}
rel_comp %>%
  group_by(task) %>%
  summarise(mean_sample_size = mean(sample_size),
            sem_sample_size = sem(sample_size)) %>%
  ggplot(aes(task,mean_sample_size,col=task))+
  geom_point(size=5)+
  geom_errorbar(aes(ymin=mean_sample_size-sem_sample_size, ymax=mean_sample_size+sem_sample_size), width = 0, size=2)+
  xlab("")+
  ylab("Sample size")+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))
```

@@

```{r}
rel_comp %>%
  ggplot(aes(task, retest_reliability, fill = task))+
  geom_boxplot()+
  theme(legend.position = 'none',
        axis.text.x = element_text(size=14),
        axis.title.y = element_text(size=14))+
  xlab("")+
  ylab("Mean icc2.1")+
  ylim(-0.4,1)
```

@@

# lit_emp_cor_out = plyr::rdply(100, lit_emp_cor)

# write.csv(lit_emp_cor_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/lit_emp_cor_out.csv')
```

@@

sample one row per measure out of lit review
r^2 of retest_reliability ~ sampled_reliability vs.
r^2 of retest_reliability ~ mean_icc2.1

coef of retest_reliability ~ sampled_reliability vs.
coef of retest_reliability ~ mean_icc2.1

@@

# comp_lit_pred_out = plyr::rdply(1000, comp_lit_pred(rel_comp))

# write.csv(comp_lit_pred_out,'/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/tables/comp_lit_pred_out.csv')
```

@@

Though we are primarily reporting icc2.1's as our metric of reliability the results don't change depending on the metric chosen. Here we plot point estimates of three different reliability metrics against each other (icc2.1, Pearson, Spearman). The bootstrapped version is essentially the same but the plots are busier due to more datapoints.

```{r}
rel_df = make_rel_df(t1_df = test_data, t2_df = retest_data, metrics = c('spearman', 'icc2.1','icc3.k', 'pearson', 'var_breakdown', 'partial_eta', 'sem'))

rel_df$task = 'task'
rel_df[grep('survey', rel_df$dv), 'task'] = 'survey'
rel_df[grep('holt', rel_df$dv), 'task'] = "task"
rel_df = rel_df %>%
  select(dv, task, spearman, icc2.1,icc3.k, pearson, partial_eta, sem, var_subs, var_ind, var_resid)
```

@@

```{r}
cor(rel_df[,c('spearman', 'icc2.1', 'icc3.k', 'pearson')])
```

Note: Some variables have <0 icc2.1's. This would be the case if the $MS_{error}$>$MS_{between}$. Data for these variables have no relationship between the two time points.

@@

```{r message=FALSE, warning=FALSE}
boot_df %>%
  group_by(dv) %>%
  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975)) %>%
  datatable() %>%
  formatRound(columns=c('icc2.1_median', 'icc2.1_2.5', 'icc2.1_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

@@

boot_df %>%
  group_by(task) %>%
  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
            spearman_median = quantile(spearman, probs = 0.5),
            spearman_2.5 = quantile(spearman, probs = 0.025),
            spearman_97.5 = quantile(spearman, probs = 0.975),
            num_vars = n()/1000) %>%
  datatable() %>%
  formatRound(columns=c('icc2.1_median', 'icc2.1_2.5', 'icc2.1_97.5', 'spearman_median', 'spearman_2.5', 'spearman_97.5'), digits=3)
```

```{r eval=FALSE}
summary(icc2.1_by_task_model)
```

@@

```{r}
summary(MCMCglmm(icc2.1 ~ task, data=rel_df, verbose=F))
```

@@

The quantiative explanation for the difference in reliability estimates between surveys and tasks, as recently detailed by Hedge et al. (2017), lies in the difference in sources of variance between these measures. Specifically, the icc2.1 is calculated as the ratio of variance between subjects variance to all sources of variance. Thus, measures with high between subjects variance would have high test-retest reliability. Intuitively, measures with high between subjects variance are also better suited for individual difference analyses as they would capture the differences between the subjects in a sample.

@@

# summary(var_subs_pct_by_task_model)

rel_df = rel_df %>% 
  mutate(var_subs_pct = var_subs/(var_subs+var_ind+var_resid)*100,
                             var_ind_pct = var_ind/(var_subs+var_ind+var_resid)*100,
                             var_resid_pct = var_resid/(var_subs+var_ind+var_resid)*100)

summary(MCMCglmm(var_subs_pct ~ task, data=rel_df, verbose=F))
```

@@

```{r}
# summary(var_ind_pct_by_task_model)

summary(MCMCglmm(var_ind_pct ~ task, data=rel_df, verbose=F))
```

```{r}
# summary(var_resid_pct_by_task_model)

summary(MCMCglmm(var_resid_pct ~ task, data=rel_df, verbose=F))
```

@@

## Task Reliabilities

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  left_join(boot_df[,c("dv", "icc2.1")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2) %>%
  group_by(task_name) %>%
  summarise(median_icc2.1 = median(icc2.1),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc2.1)

tmp %>%
  datatable() %>%
  formatRound(columns=c('median_icc2.1','icc2.1_2.5','icc2.1_97.5'), digits=3)
```

@@

Does number of items in a task have a significant effect on the average icc2.1 of meaningful measures for all trials from a task? No.

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'task',
         dv %in% meaningful_vars) %>%
  # left_join(boot_df[,c("dv", "icc2.1")], by = 'dv') %>%
  left_join(rel_df[,c("dv", "icc2.1")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

#summary(icc2.1_by_num_trials_model)
summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=F))
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc2.1))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("icc2.1")
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv),
         contrast = ifelse(overall_difference == "difference", "contrast", "non-contrast")) %>%
  filter(ddm_task == 1,
         rt_acc != 'other') %>%
  drop_na() %>%
  # left_join(boot_df[,c("dv", "icc2.1")], by = 'dv')
  left_join(rel_df[,c("dv", "icc2.1")], by = 'dv')

tmp_save = tmp %>%
  drop_na() %>% #try removing this in final release
  group_by(contrast, raw_fit, rt_acc) %>%
  summarise(icc2.1_median = quantile(icc2.1, probs = 0.5),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
            num_vars = n()/1000)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('icc2.1_median', 'icc2.1_2.5', 'icc2.1_97.5'), digits=3)
```

@@

```{r}
# summary(lmerTest::lmer(icc2.1 ~ contrast + (1|dv) ,tmp))
# summary(MCMCglmm(icc2.1 ~ contrast, random = ~ dv, data=tmp, verbose=FALSE))
summary(MCMCglmm(icc2.1 ~ contrast, data=tmp, verbose=FALSE))
```

@@

```{r}
# summary(icc2.1_by_rawfit_noncon_model)
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "non-contrast"), verbose=FALSE))
```

@@

```{r}
# summary(icc2.1_by_rawfit_con_model)
summary(MCMCglmm(icc2.1 ~ raw_fit, data=tmp %>% filter(contrast == "contrast"), verbose=FALSE))
```

@@

```{r}
tmp %>%
  group_by(contrast) %>%
  summarise(mean_icc2.1 = mean(icc2.1),
            sd_icc2.1 = sd(icc2.1))
```

@@

```{r warning=FALSE, message=FALSE}
tmp = measure_labels %>%
  mutate(dv = as.character(dv)) %>%
  filter(task == 'survey') %>%
  # left_join(boot_df[,c("dv", "icc2.1")], by = 'dv') %>%
  left_join(rel_df[,c("dv", "icc2.1")], by = 'dv') %>%
  separate(dv, c('task_name', 'extra_1', 'extra_2'), sep = '\\.',remove=FALSE) %>%
  select(-extra_1, -extra_2)

tmp_save = tmp %>%
  group_by(task_name) %>%
  summarise(median_icc2.1 = median(icc2.1),
            icc2.1_2.5 = quantile(icc2.1, probs = 0.025),
            icc2.1_97.5 = quantile(icc2.1, probs = 0.975),
            num_measures = n()/1000,
            mean_num_trials = round(mean(num_all_trials)))%>%
  arrange(-median_icc2.1)

tmp_save %>%
  datatable() %>%
  formatRound(columns=c('median_icc2.1', 'icc2.1_2.5','icc2.1_97.5'), digits=3)
```

@@

Does number of items in a survey have a significant effect on the average icc2.1 of survey measures? No.

```{r warning=FALSE, message=FALSE}
# summary(lmerTest::lmer(icc2.1 ~ num_all_trials + (1|dv), data = tmp))
summary(MCMCglmm(icc2.1 ~ num_all_trials, data=tmp, verbose=FALSE))
```

```{r warning=FALSE, message=FALSE}
tmp %>%
  ggplot(aes(num_all_trials, icc2.1))+
  geom_point()+
  geom_smooth(method="lm")+
  theme_bw()+
  xlab("Number of trials")+
  ylab("icc2.1")
```
